A template for the \emph{arxiv} style

### 2021-08-10 main/main.Rmd
cubble structure para

@@

Intro to cubble:

- list-column: rowwise_df with temporal variables, including the time index, nested. 
  - Focus on spatio: those output per station

- long form: grouped_df 
  - Focus on temporal

Compatible with tidyverse manipulation and tsibble

@@

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.path = "figures/")
library(cubble)
```

@@

In spatio-temporal data, a variable is usually either group-related or time-related. While time-related variables record variables that change in time, group-related variables are invariant to the time and have only one value per group. A cubble simplifies the workflow in spatio-temporal data through managing group and time-related variables separately in two forms: list-column and long form. The list column form:

  - defines each group in a row, 
  - displays the group-related variables in columns, and 
  - nests all the time-related variables into a column called `ts`.

In the long form,

  - each combination of group and timestamp occupies a row
  - time-related variables are displayed, and 
  - group-related variables are not explicitly displayed but can be accessed through the `meta` attribute

Below are the how the list-column and long form look like for Australia climate data, which records daily precipitation, maximum and minimum temperature for 55 stations across Australia from 2015- 2020.

\newpage

```{r echo = FALSE}
climate_small
```

```{r echo = FALSE}
climate_small %>% zoom()
```

@@

## Cubble verbs

### 2021-08-10 main/main.tex
cubble structure para

Intro to cubble:

\begin{itemize}
\tightlist
\item
  list-column: rowwise\_df with temporal variables, including the time
  index, nested.

  \begin{itemize}
  \tightlist
  \item
    Focus on spatio: those output per station
  \end{itemize}
\item
  long form: grouped\_df

  \begin{itemize}
  \tightlist
  \item
    Focus on temporal
  \end{itemize}
\end{itemize}

Compatible with tidyverse manipulation and tsibble

@@

>>>>

In spatio-temporal data, a variable is usually either group-related or
time-related. While time-related variables record variables that change
in time, group-related variables are invariant to the time and have only
one value per group. A cubble simplifies the workflow in spatio-temporal
data through managing group and time-related variables separately in two
forms: list-column and long form. The list column form:

\begin{itemize}
\tightlist
\item
  defines each group in a row,
\item
  displays the group-related variables in columns, and
\item
  nests all the time-related variables into a column called \texttt{ts}.
\end{itemize}

In the long form,

\begin{itemize}
\tightlist
\item
  each combination of group and timestamp occupies a row
\item
  time-related variables are displayed, and
\item
  group-related variables are not explicitly displayed but can be
  accessed through the \texttt{meta} attribute
\end{itemize}

Below are the how the list-column and long form look like for Australia
climate data, which records daily precipitation, maximum and minimum
temperature for 55 stations across Australia from 2015- 2020.

\newpage

\begin{verbatim}
## # Cubble: station-wise: list-column
## # Group:  station [55]
## # Meta:   station [fct], lat [dbl], long [dbl], elevation [dbl], name [fct]
##    station       lat  long elevation name                ts                  
##    <fct>       <dbl> <dbl>     <dbl> <fct>               <list>              
##  1 ASN00001019 -14.3  127.      23   kalumburu           <tbl_ts [2,147 x 4]>
##  2 ASN00002012 -18.2  128.     422   halls creek airport <tbl_ts [2,191 x 4]>
##  3 ASN00003003 -17.9  122.       7.4 broome airport      <tbl_ts [2,192 x 4]>
##  4 ASN00006011 -24.9  114.       4   carnarvon airport   <tbl_ts [2,192 x 4]>
##  5 ASN00009021 -31.9  116.      15.4 perth airport       <tbl_ts [2,192 x 4]>
##  6 ASN00009193 -32.0  116.      43.1 rottnest island     <tbl_ts [2,192 x 4]>
##  7 ASN00009518 -34.4  115.      13   cape leeuwin        <tbl_ts [2,184 x 4]>
##  8 ASN00009789 -33.8  122.      25   esperance           <tbl_ts [2,187 x 4]>
##  9 ASN00010286 -31.6  117.     217.  cunderdin airfield  <tbl_ts [2,190 x 4]>
## 10 ASN00010917 -32.7  117.     275   wandering           <tbl_ts [2,192 x 4]>
## # ... with 45 more rows
\end{verbatim}

\begin{verbatim}
## # Cubble: time-wise: long form [tsibble]
## # Group:  station [55]
## # Meta:   station [fct], lat [dbl], long [dbl], elevation [dbl], name [fct]
##    station     date        prcp  tmax  tmin
##    <fct>       <date>     <dbl> <dbl> <dbl>
##  1 ASN00001019 2015-01-01   164  31.5  25  
##  2 ASN00001019 2015-01-02   124  31.3  25  
##  3 ASN00001019 2015-01-03    50  29.2  24.7
##  4 ASN00001019 2015-01-04   204  32.1  24.3
##  5 ASN00001019 2015-01-05   412  31.4  24.6
##  6 ASN00001019 2015-01-06   200  28.7  25.1
##  7 ASN00001019 2015-01-07   822  30.2  24.5
##  8 ASN00001019 2015-01-08    22  31    26.6
##  9 ASN00001019 2015-01-09    62  32.7  26.2
## 10 ASN00001019 2015-01-10   274  32.9  22.6
## # ... with 120,311 more rows
\end{verbatim}

@@

\hypertarget{cubble-verbs}{%
\subsection{Cubble verbs}\label{cubble-verbs}}
